On Secure Delegation of SampBQP with a Classical Client

### 2020-01-23 preliminaries.tex
Make a pass at preliminary

\begin{rmk}
\hannote{sampling generalize decision blah}
\end{rmk}

@@

\begin{dfn}
	A quantum homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
	\begin{itemize}
		\item $\mathsf{Keygen}(1^\lambda)\rightarrow(pk, evk, sk)$
		\item $\mathsf{Enc}_{pk}(\mu)\rightarrow c$
		\item $\mathsf{Dec}_{sk}(c)\rightarrow \mu^*$
			\Ethan{Urmila didn't specify that $\mathsf{Dec}\circ\mathsf{Enc}=Id$}
		\item $\mathsf{Eval}_{evk}(f, c_1, \ldots, c_l)\rightarrow c_f$
	\end{itemize}
\end{dfn}

@@

As this is a homomorphic encryption scheme, it satisfies $$\mathsf{HE.Dec}_{sk}(c_f)=f(\mathsf{HE.Dec}_{sk}(c_0),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$ with all but negligible probability in $\lambda$

@@

Lastly, we generalize the above security definition to interactive schemes.

\begin{dfn}
	Let $(\bbP, \bbV)(x)$ be an interactive protocol with the verifier's initial input being $x$. Then it is IND-CPA secure if any polynomial time adversary $\cA$ can't win \protoref{protoIndCPA} with probability better than $\frac{1}{2}+\negl(\lambda)$ \Ethan{Check if it's actually lambda}
\end{dfn}

\floatname{algorithm}{Protocol}
\begin{algorithm}
	\caption{ $\QPIP_1$ protocol for $\SampBQP$}
	\label{ProtoQPIP1}
	\begin{algorithmic}[1]
		\State \Ethan{Do we need some kinda generalization of Keygen here...?}
		\State $\cA$ picks strings $c_1$ and $c_2$ and sends them to the challenger
		\State The challenger picks $c_b$ at random where $b\in\set{0,1}$
		\State The challenger runs the protocol with the adversary, acting as the verifier with input $c_b$
		\State $\cA$ attempts to guess $b$
	\end{algorithmic}
\end{algorithm}
\floatname{algorithm}{Algorithm}

>>>>

\hannote{sampling generalize decision blah} \Ethan{That doesn't sound right}

@@

\begin{dfn}
	A quantum homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
	\begin{itemize}
		\item $\mathsf{Keygen}(1^\lambda)\rightarrow(pk, evk, sk)$
		\item $\mathsf{Enc}_{pk}(\mu)\rightarrow c$
		\item $\mathsf{Dec}_{sk}(c)\rightarrow \mu^*$
		\item $\mathsf{Eval}_{evk}(f, c_1, \ldots, c_l)\rightarrow c_f$
	\end{itemize}
\end{dfn}

@@

$\mathsf{HE}$ also satisfies, with all but negligible probability in $\lambda$, that
$$\mathsf{HE.Dec}_{sk}(\mathsf{Eval}_{evk}(f, c_1, \ldots, c_l)=f(\mathsf{HE.Dec}_{sk}(c_0),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$

@@

\subsection{Security definition for interactive protocols}

\begin{dfn}
	Let $\lambda$ be a security parameter.
	Let $(\bbP, \bbV)(x)$ be an interactive protocol with the verifier's initial input being $x$.
	Then it is IND-CPA secure if any polynomial time adversary $\cA$ can't win \myprotoref{protoIndCPA} with probability better than $\frac{1}{2}+\negl(\lambda)$ \Ethan{Check if it's actually lambda}
\end{dfn}

\floatname{algorithm}{Protocol}
\begin{algorithm}
	\caption{ $\QPIP_1$ protocol for $\SampBQP$}
	\label{ProtoIndCPA}
	\begin{algorithmic}[1]
		\State $\cA$ picks strings $c_1$ and $c_2$ and sends them to the challenger
		\State The challenger picks $c_b$ at random where $b\in\set{0,1}$
		\State The challenger runs the protocol with the adversary, acting as the verifier with input $c_b$
		\State $\cA$ attempts to guess $b$
	\end{algorithmic}
\end{algorithm}
\floatname{algorithm}{Algorithm}

\begin{rmk}
	\Ethan{Maybe something about this being (hopefully) equivalent to simulator-based security?}
\end{rmk}
